Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-03-18 paper/plos.tex
tiny change on paper Tested everything on crystal.

    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
      then we and you observe it growing in a .25 micron flexible
      channel, it presumably must be able to grow because it deformed
      the channel to larger than .3 microns.}
  \item \blue{David} Starry night in the wild-type cells is a problem.
  \item Better explanation of correlation function (which is
    interesting!).
  \item Shape A is the interesting bit in our main figure.
  \item Would like more analysis of stochastic locations in different
    geometries.  Clusters?  Could add more geometries?
  \item Bold conclusions about flattening.  Talk about both width and
    thickness.  Compare Halatek 2012.  Wants systematically more
    geometries again.
  \item Is doubtful of our correlation plots relative to those of
    Fange and Elf 2006.
  \item Clarify (esp in conclusions) what we mean by flattening and
    irregular shape.  ``breaking the cylindrical symmetry and
    flattening the cells.'' versus ``breaking the mirror plane
    symmetry of the cross-section of a flattned cell.''
  \item[TODO suggestion] Switch to Halatek and Frey
  \item[TODO suggestion] Thoroughly explor shape parameter space
  \item[TODO suggestion] Check robustness of our conclusions with
    respect to changes in (reaction-diffusion?) parameters.
  \item Check order of figures and their references.
  \item Cite biological (non-computational) works e.g. Corbin 2008.
  \end{enumerate}
  Second referee:
  \begin{enumerate}
  \item Nitpicks about language of deterministic model versus
    stochastic model.  (Read carefully)
  \item \blue{David} Explain in greater detail the obviousness (maybe) that the
    deterministic approach doesn't have fluctuations.  RESPOND:
    chaotic systems do deterministically result in fluctuations.
    Explain this somewhere, and discuss triviality of the conclusion
    that deterministic is wrong because it does not exhibit these
    irregularities.
  \item Would like temporal averages over cell-cycle time scales.
  \item More discussion of how flattening leads to spatial
    irregularities.  Compare with large nearly spherical e. coli Shih
    2005.  See also Halatek and Frey 2012 for rotating oscillation
    axis due to destabilization of short modes.  How does this connect
    with our stability analysis?
  \item \blue{David} Should mention more recent revisions of the model.
  \item Fange and Elf do not use the same reaction-diffusion
    equations.
  \item Clarify statement about 1000 proteins and stochastic
    fluctuation.  Reword about a continuum description omitting
    information?
  \item \blue{Done} Do not call Huang parameters ``wild type values.''  They are
    fitted parameters.
  \item Add methods section for numerics (deterministic).
  \item \blue{Done} Add details of the linear stability analysis.
  \item \blue{David} Still need to fix periods on.  \blue{About this
    point - I updated the data and it seems the result is defferent
    from before - the stadium shapes seem to be temporally correlated
    for much longer compared with the shape A than before.}
    correlation plots
  \end{enumerate}
}

>>>>

    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
      then we and you observe it growing in a .25 micron flexible
      channel, it presumably must be able to grow because it deformed
      the channel to larger than .3 microns.}
  \item \blue{David} Starry night in the wild-type cells is a problem.
  \item Better explanation of correlation function (which is
    interesting!).
  \item Shape A is the interesting bit in our main figure.
  \item Would like more analysis of stochastic locations in different
    geometries.  Clusters?  Could add more geometries?
  \item Bold conclusions about flattening.  Talk about both width and
    thickness.  Compare Halatek 2012.  Wants systematically more
    geometries again.
  \item Is doubtful of our correlation plots relative to those of
    Fange and Elf 2006.
  \item Clarify (esp in conclusions) what we mean by flattening and
    irregular shape.  ``breaking the cylindrical symmetry and
    flattening the cells.'' versus ``breaking the mirror plane
    symmetry of the cross-section of a flattned cell.''
  \item[TODO suggestion] Switch to Halatek and Frey
  \item[TODO suggestion] Thoroughly explor shape parameter space
  \item[TODO suggestion] Check robustness of our conclusions with
    respect to changes in (reaction-diffusion?) parameters.
  \item Check order of figures and their references.
  \item Cite biological (non-computational) works e.g. Corbin 2008.
  \end{enumerate}
  Second referee:
  \begin{enumerate}
  \item Nitpicks about language of deterministic model versus
    stochastic model.  (Read carefully)
  \item \blue{David} Explain in greater detail the obviousness (maybe) that the
    deterministic approach doesn't have fluctuations.  RESPOND:
    chaotic systems do deterministically result in fluctuations.
    Explain this somewhere, and discuss triviality of the conclusion
    that deterministic is wrong because it does not exhibit these
    irregularities.
  \item Would like temporal averages over cell-cycle time scales.
  \item More discussion of how flattening leads to spatial
    irregularities.  Compare with large nearly spherical e. coli Shih
    2005.  See also Halatek and Frey 2012 for rotating oscillation
    axis due to destabilization of short modes.  How does this connect
    with our stability analysis?
  \item \blue{David} Should mention more recent revisions of the model.
  \item Fange and Elf do not use the same reaction-diffusion
    equations.
  \item Clarify statement about 1000 proteins and stochastic
    fluctuation.  Reword about a continuum description omitting
    information?
  \item \blue{Done} Do not call Huang parameters ``wild type values.''  They are
    fitted parameters.
  \item Add methods section for numerics (deterministic).
  \item \blue{Done} Add details of the linear stability analysis.
  \item \blue{David} Still need to fix periods on correlation plots.
    \blue{About this point - I updated the data and it seems the
      result is defferent from before - the stadium shapes seem to be
      temporally correlated for much longer compared with the shape A
      than before.}
  \end{enumerate}
}
